\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% --- FONT OPTIONS ---
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% \usepackage{CormorantGaramond}
% \usepackage{charter}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.1pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\bfseries\raggedright\large
}{}{0em}{}[\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% --- CUSTOM COMMANDS ---
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% --- RESUME STARTS HERE ---

\begin{document}

% --- HEADING ---
\begin{center}
    \textbf{\Huge AVULA PUNITH KUMAR REDDY} \\ \vspace{1pt}
    \small +91-93908 82204 $|$ \href{mailto:punithkumar1732003@gmail.com}{\underline{punithkumar1732003@gmail.com}} $|$ 
    \href{https://github.com/puni7777777}{\underline{github.com/puni7777777}}
\end{center}

% --- PROFESSIONAL SUMMARY ---
\section{Professional Summary}
Dynamic Mechanical Design Engineer with 1+ years of hands-on experience in CAD modeling, product design, and engineering analysis at Bharat Electronics Limited. Expert in SolidWorks, AutoCAD, and GD\&T for developing precision components and assemblies that meet stringent manufacturing standards. Demonstrated success in applying DFM principles to optimize designs, resolve production challenges, and contribute to cost-effective solutions while ensuring compliance and quality excellence.

% --- TECHNICAL SKILLS ---
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{CAD/Modeling}: SolidWorks, AutoCAD, CATIA V5, Siemens NX}
    \resumeItem{\textbf{Design Skills}: 3D Modeling, Assembly Design, GD\&T, Sheet Metal, Welding}
    \resumeItem{\textbf{Analysis \& Simulation}: SolidWorks Simulation, ANSYS (Basic)}
    \resumeItem{\textbf{Tools}: MS Office Suite, ERP Systems (SAP)}
  \resumeItemListEnd

% --- EXPERIENCE ---
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bharat Electronics Limited}{Hyderabad, Telangana}
      {Mechanical Design Engineer}{Feb 2025 -- Present}

      \resumeItemListStart
        \resumeItem{Developed detailed 3D models and 2D manufacturing drawings for mechanical components using SolidWorks and AutoCAD, ensuring 100\% compliance with industry standards.}
        \resumeItem{Collaborated with the manufacturing team to resolve production bottlenecks.}
        \resumeItem{Applied Geometric Dimensioning and Tolerancing (GD\&T) to ensure precision and interchangeability of complex parts in multi-component assemblies.}
        \resumeItem{Maintained and updated Bill of Materials (BOM) for multiple product lines within the ERP system, ensuring procurement accuracy.}
        \resumeItem{Conducted static load analysis using SolidWorks Simulation to validate design integrity under operating conditions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% --- EDUCATION ---
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {JNTUH-UCES}{Sangareddy, Telangana}
      {Bachelor of Technology in Mechanical Engineering; CGPA: 6.9/10.0}{2024}
      \resumeSubheading
        {Sri Chaitanya Jr kalashala}{Hyderabad, Telangana}
        {Intermediate; Percentage: 91.4\%}{2018 - 2020}
      \resumeSubheading
        {Unique High School}{Hyderabad, Telangana}
        {10th Class; CGPA: 9.7/10.0}{2018}
  \resumeSubHeadingListEnd

% --- PROJECTS ---
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Bladeless Fan using Ion Wind} $|$ \emph{SolidWorks, Electrohydrodynamics}}{}
      \resumeItemListStart
        \resumeItem{Designed and prototyped a bladeless fan utilizing Ion Wind (Ion thrust) to generate airflow through high-voltage corona discharge, eliminating the need for moving parts.}
        \resumeItem{Engineered and optimized emitter and collector electrode geometries in SolidWorks to maximize airflow velocity and structural stability.}
        \resumeItem{Conducted experimental analysis to quantify the relationship between voltage input and airflow output.}
        \resumeItem{Integrated high-voltage power supplies and fabricated a specialized housing using FDM 3D printing (PLA) to ensure robust electrical insulation, structural integrity, and user safety.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
% --- END OF RESUME ---

\end{document}

